Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
figures quivers of dissections
Curves and walks.

% non-kissing complex, lattice, flip graph
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex

@@

Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{dissections}}
	\caption{Some pairs of dual dissections on different surfaces.}
	\label{fig:dissections}
\end{figure}

@@

\subsection{Non-crossing and non-kissing complexe coincide}

>>>>

% non-kissing complex, lattice, flip graph
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)

@@

\begin{example}
Two examples of dual cellular dissections on a surface are represented in \fref{fig:dissections}.
\end{example}

@@

\subsection{Non-crossing and non-kissing complexes coincide}

Let~$\bar Q$ be a locally gentle bound quiver.

\begin{definition}
\label{def:curveOfAWalk}
Let~$\omega$ be a (possibly infinite) walk on~$\bar Q$. 
Define a curve~$\curveof(\omega)$
\end{definition}
